\documentclass[11pt,a4paper]{moderncv}
\usepackage{palatino,paralist}
\usepackage{enumitem}
\usepackage{comment}
% moderncv themes
\moderncvtheme[black]{classic}               

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.875]{geometry}
\setlength{\hintscolumnwidth}{3.4cm}		% if you want to change the width of the column with the dates


\AfterPreamble{\hypersetup{
  pdfauthor={Erin Ellefsen},
 pdftitle={CV for Erin Ellefsen},
 pdfsubject={Detailed CV for Erin},
  urlcolor=blue,
}}

% personal data
\firstname{Erin}
\familyname{Ellefsen}
\address{St. Olaf College}   
\email{ellefs2@stolaf.edu}                     
\extrainfo{506 7th Street E\\
Northfield, MN 55057}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

%----------------------------------- content -----------------------------------------------
\begin{document}
\maketitle

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{August 2022}{PhD in Applied Mathematics}{University of Colorado Boulder}{GPA 3.9}{}{}
\cventry{December 2020}{Masters of Science in Applied Mathematics}{University of Colorado Boulder}{GPA 3.9}{}{}
\cventry{May 2017}{Bachelors of Arts}{Mathematics, Minor in Computer Science}{Luther College}{ GPA 3.9}{}



%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCES	
%----------------------------------------------------------------------------------------


\section{Teaching Experience}

\cventry{Fall 2024 - Present}{Assistant Professor of Mathematics}{St. Olaf College}{}{}{}
\begin{itemize}[leftmargin=4cm]
	\item MATH 330, Differential Equations II, Fall 2024, Spring 2025
	\item MATH 230, Differential Equations I, Fall 2024, Spring 2025
\end{itemize}

\cventry{2022 - 2024}{Assistant Professor of Mathematics}{Earlham College}{}{}{}
\begin{itemize}[leftmargin=4cm]
	\item MATH 330, The Art and Science of Mathematical Modeling, Spring 2023
	\item MATH 320, Differential Equations, Fall 2022, Fall 2023
	\item MATH 300, Mathematical Statistics, Fall 2022, Fall 2023
	\item MATH 180, Calculus A, Spring 2023
	\item MATH 120, Elementary Statistics, Spring 2023
	\item ESEM 150, Don't Get Duped: \textit{Reasoning Mathematically in an age of digital lies}, Fall 2023
\end{itemize}





\cventry{2018-2019}{Lead Teaching Assistant}{University of Colorado Boulder}{}{}{Attended Lead TA training, led a year-long teaching and research seminar for first year graduate students, performed Video Teaching Consultations for Teaching Assistants within and outside of the department, completed a year-long video project for the Center for Teaching and Learning.}

\cventry{2017-2021}{Graduate Teaching Assistant}{University of Colorado Boulder Mathematics Department}{}{}{Led weekly recitations for undergraduates, held
	weekly office hours, created homework rubrics, led exam review sessions, graded homeworks and exams, wrote homework solutions.}
\begin{itemize}[leftmargin=4cm]
	\item APPM 1350, Calculus I for Engineers, Summer 2018, Fall 2018
	\item APPM 1360, Calculus II for Engineers, Fall 2017, Spring 2018
	\item APPM 2360, Differential Equations, Fall 2019, Fall 2021
	\item APPM 4440, Applied Analysis, Fall 2020
	\item APPM 3570, Applied Probability, Spring 2021
\end{itemize}

\cventry{Fall 2019}{Grader}{University of Colorado Boulder Applied Mathematics Department}{}{}{Graded homework for APPM 5470: Partial Differential and Integral Equations, a graduate course covering properties and solutions of partial differential equations: methods of characteristics, well-posedness, wave, heat, and Laplace equations, Green's functions and related integral equations.}




%\cventry{2015-2017}{Student Tutor and Grader}{Luther College Mathematics Department}{}{}{Graded and tutored students in a variety of subjects including Calculus I, II, and Elementary Number Theory.}



\section{Research Experience}

\cventry{2024 - Present}{Mathematical Biology Research Group}{St. Olaf College}
{}{}{We are using PDEs and ODEs to understand how diffusion strategies affect persistence of a population under environmental disturbance, drift, and habitat fragmentation. This project incorporates experimental data on habitat fragmentation.}

\cventry{2022 - 2024}{Mathematical Biology Research Group}{Earlham College}
{}{}{Of interest is a nonlocal systems of PDEs. These are used to study territory development and management strategies of invasive species. A system of ODEs is used to study the dynamics of a fish population with enhanced female cannibalism. The latter is a project that involves undergraduate students. }


\cventry{2018- 2022}{Graduate Research Assistant}{University of Colorado Boulder}{}{}{A system of nonlocal PDEs with cross diffusion was used to model territory formation in meerkats. Equilibrium solutions were used to incorporate data into the model. Developed theory for a nonlocal PDE modeling a birth-jump process that can be used to model fire propogation, cancer cell growth, or seed germination.  }
\begin{comment}
\cventry{Summer 2016}{Student Researcher}{Oregon State University Mathematics REU}{}{}{Generalized one row of a catalog of mock modular forms developed by Folsom, Garthwaite, et. al to an infinite class and showed that the functions in this infinite class are mock modular forms.}

\cventry{Summer 2015}{Student Researcher}{Luther College Summer Research Grant}{}{}{Developed a computer simulation of disease spread in a population based off of the SIR model. Investigated when the continuous SIR model would predict an epidemic compared to when our discrete computer simulation would predict one. Investigated the effect of clustering and vaccination strategies.}
\end{comment}
%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications}

\cvitem{2023}{Erin Ellefsen, Nancy Rodr\'iguez; \emph{"Nonlocal Mechanistic Models in Ecology: Numerical Methods and Parameter Inference"}, Applied Sciences, 2023}

\cvitem{2021}{Erin Ellefsen, Nancy Rodr\'iguez; \emph{"On equilibrium solutions to nonlocal mechanistic models in ecology"}, Journal of Applied Analysis and Computation, 2021}

\cvitem{ 2020}{Erin Ellefsen, Nancy Rodr\'iguez; \emph{"On some theory of monostable and bistable pure birth-jump integro-differential equations"}, Ecological Complexity, 2020 }  

\cvitem{2019}{Allison Arnold-Roksandich, Brian Diaz, Erin Ellefsen, Holly Swisher; \emph{"Extending a catalog of mock and quantum modular forms to an infinite class"}, Research in Number Theory, 2019.} 


%----------------------------------------------------------------------------------------
%	PRESENTATIONS	
%----------------------------------------------------------------------------------------


\section{Selected Presentations}

\begin{itemize}[leftmargin=3.75cm]
	\item[] \textbf{"Two-species competition with $p$-Laplacian diffusion"}
\end{itemize}
\vspace{-.3cm}
\cvitem{Spring 2025}{AWM Research Symposium, Madison, WI}
\begin{itemize}[leftmargin=3.75cm]
\item[] \textbf{"Models in Mathematical Ecology: Territory Development, Seed Dispersal, and Invasive Species Management"}
\end{itemize}
\vspace{-.3cm}
\cvitem{Fall 2024}{Hamline University Mathematics Colloquium, Minneapolis, MN}
\cvitem{Fall 2023}{Earlham College Biology Colloquium, Earlham College, Richmond, IN}
\begin{comment}
\begin{itemize}[leftmargin=3.75cm]
	\item[] \textbf{"The Fastest People in the World: Modeling Elite 100m Sprinters"}
\end{itemize}
\vspace{-.3cm}
\cvitem{Fall 2024}{St. Olaf MSCS Showcase, Northfield, MN}
\end{comment}
\begin{itemize}[leftmargin=3.75cm]
	\item[] \textbf{"Nonlocal PDEs in Ecology: Numerical Methods and Parameter Inference"}
\end{itemize}
\vspace{-.3cm}
\cvitem{Fall 2023}{Annual Mathematics Conference, Miami University, Oxford, OH}




\begin{itemize}[leftmargin=3.75cm]
	\item[] \textbf{"Nonlocal Models in Ecology"}
\end{itemize}
\vspace{-.3cm}
\cvitem{February 2021}{Florida Women in Mathematics Day, Florida Atlantic University, Virtual}
\cvitem{Spring 2021}{Applied Mathematics Graduate Recruitment, Univeristy of Colorado Boulder, Virtual}
\cvitem{Fall 2021}{Mathematical Biology Seminar, University of Colorado Boulder, Virtual}


\begin{itemize}[leftmargin=3.65cm]
	\item[] \textbf{"Efficiently Finding Steady States of Nonlocal Territorial Models in Ecology"}
\end{itemize}
\vspace{-.3cm}
\cvitem{Spring 2022}{SIAM PD22: Recent Advances in Cross-Diffusion and Population Models, Virtual}
\cvitem{Fall 2021}{Differential Equations of Mathematical Physics and their Applications, Como, Italy}
\cvitem{Fall 2021}{Mathematical Biology Seminar, University of Iowa, Virtual}
\cvitem{July 2021}{Mathematical Congress of the Americas, Virtual Poster}
\cvitem{March 2020}{Front Range Student Conference in Applied Math, University of Colorado Denver, Denver, CO}
\cvitem{Fall 2019}{Mathematical Biology Seminar, University of Colorado Boulder, Boulder, CO}



\begin{comment}
\cventry{Spring 2019}{APPM 5480: Approximation Methods}{}{}{}{University of Colorado Boulder, Boulder, CO}
\vspace{-.5cm}
\begin{itemize}[leftmargin=4cm]
	\item "Asymptotic Methods for Traveling Wave Solutions in a Population Model"
\end{itemize}
\end{comment}
\begin{itemize}[leftmargin=3.65cm]
	\item[] \textbf{"Nonlocal Territorial Models in Ecology"}
\end{itemize}
\vspace{-.3cm}
\cvitem{September 2019}{Annual Mathematics Conference, Miami University, Oxford, OH}
\cvitem{Spring 2019}{Applied Mathematics Graduate Recruitment, University of Colorado Boulder, Boulder, CO}

\begin{comment}
\cventry{Spring 2018}{APPM 5460: Dynamical Systems and Differential Equations}{}{}{}{University of Colorado Boulder, Boulder, CO}
\vspace{-.5cm}
\begin{itemize}[leftmargin=4cm]
	\item "Modeling the Dynamics of the Wildwood Pendulum"
\end{itemize}
\end{comment}
%\begin{itemize}[leftmargin=3.65cm]
%	\item[] \textbf{"Extending a Catalog of Mock Modular Forms to an Infinite Class"}
%\end{itemize}
%\vspace{-.3cm}
%\cvitem{Spring 2017}{Luther College Research Symposium, Luther College, Decorah, IA}

%\begin{itemize}[leftmargin=3.65cm]
%	\item[] \textbf{"Investigating the Effects of Clustering and Vaccination in a Discrete SIR Model"}
%\end{itemize}
%\vspace{-.3cm}
%\cvitem{Spring 2016}{Luther College Research Symposium, Luther College, Decorah, IA}

\section{Professional Development}
\cventry{June 2025}{MSCS Professsional Development Participant and Peer Leader}{}{}{}{Participated and helped with one session of a departmental professional development series aimed as using technology such as GitHub and PreTeXt.}
\cventry{January 2024}{Special session co-organizer for Joint Math Meetings}{}{}{}{Co-organizing a special session about alternative assessment methods, in particular Team Based Inquiry Learning, with two colleagues via Project NExT.}

\cventry{Fall 2023}{Math Modeling Hub’s COMPOSTE workshop}{}{}{}{ A series of two-hour virtual workshops designed to help adapt old M3C, HiMCM, MCM/ICM, and SCUDEM contest problems into engaging lesson plans and modules at the undergraduate level}

\cventry{2023-2024}{SIAM Project NExT (New Experiences in Teaching) Fellow}{}{}{}{ A professional development program for recent Ph.D.s in the mathematical sciences which addresses all aspects of an academic career: improving the teaching and learning of mathematics, engaging in research and scholarship, finding exciting and interesting service opportunities, and participating in professional activities. It provides the participants with a network of peers and mentors as they assume these responsibilities. }
\cventry{Spring 2023}{General Education Learning Circle Participant}{Earlham College}{}{}{Participating faculty met five times in Fall 2022 and Spring 2023 to discuss assessment, including best practices, various approaches, and what assessment means at Earlham. As part of this learning circle, we produced a worksheet intended to help match assessment plans to a specific learning goal, to consider both direct and indirect measures, to provide an interpretation of the results, and to use the results to inform pedagogical choices.}
\cventry{February 2023, 2025}{SIMIODE Expo Attendee}{}{}{} {A conference for faculty, students, and other parties interested in using modeling to motivate, teach, and learn differential equations.}
\cventry{Spring 2021}{Certificate of College Teaching}{University of Colorado Boulder}{}{}{Completed my requirements to get my Certificate of College Teaching which include 20 hours of teaching workships, 20 hours of discipline-specific training, two Video Teaching Consultations, a faculty evaluation, and a teaching portfolio.}


\section{Research Support }
\cvitem{In Progress 2025}{Rana Parshad, Erin Ellefsen, Bo Zhang; \emph{Managing Competition Dynamics under Fragmentation for Enhanced Invasion Control}, NSF Mathematical Biology.
\vspace{-.15cm}\begin{itemize}
\item Competitive federal program that supports research in areas of applied and computational 
mathematics relevant to the biological and life sciences.
\end{itemize}
}
\vspace{-.25cm}
\cvitem{2025}{Erin Ellefsen; \emph{Using Differential Equations to Model Invasive Species Management}, St. Olaf College Collaborative Undergraduate Research and Inquiry Program.
\vspace{-.15cm}\begin{itemize}
\item Internal funding program that supports summer research experiences for undergraduates.
\end{itemize}}
\vspace{-.25cm}
\cvitem{2023}{Erin Ellefsen; \emph{Using Differential Equations to Investigate Invasive Species Management and Cyclical Mating Dynamics}, Earlham College Summer Collaborative Research.
\vspace{-.15cm}\begin{itemize}
\item Internal funding program that supports summer research experiences for undergraduates.
\end{itemize}}\vspace{-.75cm}

\section{Service and Community Engagement}
\cvitem{2024-2025}{MSCS Talks Committee Member, St. Olaf College, Northfield, MN}{}{}{}{}
\cvitem{Spring 2025}{Search Committee Member for a VAP in Mathematics, St. Olaf College, Northfield, MN}{}{}{}{}
\cvitem{Fall 2025}{Keynote speaker for MSCS Colloquium, St. Olaf College, Northfield, MN}{}{}{}{}
\cvitem{2024-2025}{Faculty Representative for SIAM and AWM clubs, St. Olaf College, Northfield, MN}{}{}{}{}
\cvitem{2023-2024}{Volunteer Cross Country Coach, Earlham College, Richmond, IN}{}{}{}{}
\cvitem{2023-2024}{Faculty Member on Student Conduct Council, Earlham College, Richmond, IN}{}{}{}{}
\cvitem{2022-2024}{Re-Launched Earlham's Chapter of Association for Women in Mathematics
\vspace{-.1cm}
\begin{itemize}
\item Association of Women in Mathematics (AWM) is a group for gender-minorities in mathematics. Planned activities have included:  AWM lunches in the dining hall several times a semester, weekend pizza gatherings, an AWM bowling event, and a career panel.
\end{itemize}}
\vspace{-.25cm}
\cvitem{AY 2022-2023}{Assisting Volleyball Graduate Assistant with team statistics
\vspace{-.15cm}\begin{itemize}
\item Attended various meetings with Cal Pringle to share statistics expertise in regards to volleyball data, guide possible analyses that will help advise training, and share data that could possibly be used as examples and projects in the statistics classroom.
\end{itemize}}\vspace{-.35cm}
\cvitem{Spring 2023 }{Assisted in writing and grading the Mathematics Department's comprehensive exams}
\cvitem{Spring 2023 }{Late Night Breakfast Volunteer Server}
\cvitem{Spring 2023}{Search Committee Member for Biology's Quantitative Plant Ecologist}
%\cvitem{Fall 2023}{Volunteer Cross Country Coa
\cvitem{2018 - 2021}{Volunteer Cross Country \& Track Coach, Standley Lake High School, Westminster, CO}{}{}{}{}

\section{Technical Skills}
\cvitem{}{MatLab, Python, Mathematica, limited experience with PETSc }
%----------------------------------------------------------------------------------------
%	Honors and Awards	
%----------------------------------------------------------------------------------------
\section{Scholarships and Awards}
\cventry{2023-2024}{
SIAM Project NExT Fellow}{}{}{}{}
\cventry{2017-2020}{
R.J McElroy Fellowship}{}{}{}{}

\cventry{May 2017}{Phi Beta Kappa}{}{}{}{}
\cventry{2013-2017}{Dean's List}{Luther College}{}{}{}
\cventry{}{Carl Strom Prize in Mathematics}{Luther College}{}{}{}
\cventry{}{Women in Math \& Statistics Scholarship}{Luther College}{}{}{}
\cventry{}{Ann Lee Moilien Memorial Math Scholarship}{Luther College}{}{}{}
\cventry{}{Cory L. Braun Memorial Math Scholarship}{Luther College}{}{}{}
\cventry{}{Paul G. And Hazel H. Hoel Math Scholarship}{Luther College}{}{}{}


%----------------------------------------------------------------------------------------
%	PROFESSIONAL MEMBERSHIPS
%----------------------------------------------------------------------------------------

\section{Professional Memberships}
\cvitem{}{Mathematical Association of America}
\cvitem{}{Association of Women in Mathematics}
\cvitem{}{Society of Applied and Industrial Mathematics}
\begin{comment}
\section{Undergraduate Memberships}

\cvitem{2013-2016}{Luther College Cross Country Team, \emph{Team Captain, 2016}}
\cvitem{2014-2017}{Luther College Track \& Field Team, \emph{Team Captain, 2017}}
\cvitem{2016-2017}{Student Athlete Advisory Committe}
\cvitem{2015-2017}{Math Club}
\cvitem{2017}{Senior Giving Campaign}
\end{comment}

\end{document}

