\documentclass[11pt,a4paper]{moderncv}
\usepackage{palatino,paralist}
\usepackage{enumitem}
\usepackage{comment}
% moderncv themes
\moderncvtheme[black]{classic}               

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.875]{geometry}
\setlength{\hintscolumnwidth}{3.4cm}		% if you want to change the width of the column with the dates


\AfterPreamble{\hypersetup{
  pdfauthor={Erin Ellefsen},
 pdftitle={CV for Erin Ellefsen},
 pdfsubject={Detailed CV for Erin},
  urlcolor=blue,
}}

% personal data
\firstname{Erin}
\familyname{Ellefsen}
\address{Earlham College}   
\email{ellefer@earlham.edu}                     
\extrainfo{242 1/2 S 5th Street\\
Richmond, IN 47374}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

%----------------------------------- content -----------------------------------------------
\begin{document}
\maketitle
\vspace{-1cm}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
\cventry{August 2022}{PhD Applied Mathematics}{}{}{University of Colorado Boulder}{}
\cventry{December 2020}{Masters of Science in Applied Mathematics}{}{}{University of Colorado Boulder}{}
\cventry{May 2017}{Bachelors of Arts}{Magna Cum Laude}{Mathematics}{Luther College}{}
%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCES	
%----------------------------------------------------------------------------------------
\section{Post-Doctoral Academic Experience}
\cventry{Fall 2022 - Present}{Assistant Professor of Mathematics}{Earlham College}{}{}{}
\begin{itemize}[leftmargin=4cm]
	\item ES 1, How Not to Get Duped: \textit{Reasoning mathematically to find the truth in an age of digital lies}, Fall 2023
	\item MATH 120, Elementary Statistics, Spring 2023
	\item MATH 180, Calculus A, Spring 2023
	\item MATH 330, Mathematical Modeling, Spring 2023
	\item MATH 320, Differential Equations, Fall 2022, Fall 2023
	\item MATH 300, Mathematical Statistics, Fall 2022, Fall 2023
\end{itemize}



%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Publications Since Date of Hire}
\cvitem{}{Erin Ellefsen, Nancy Rodr\'iguez; \emph{"Nonlocal Mechanistic Models in Ecology: Numerical Methods and Parameter Estimation"}, Preprint, 2022.}

\section{Funding}
\cvitem{Submitted 2023}{Rana Parshad, Erin Ellefsen, Bo Zhang; \emph{Managing Competition Dynamics under Fragmentation for Enhanced Incation Control}, NSF Mathematical Biology.
\vspace{-.15cm}\begin{itemize}
\item Competitive federal program that supports research in areas of applied and computational 
mathematics relevant to the biological and life sciences.
\end{itemize}
}
\vspace{-.25cm}
\cvitem{2023}{Erin Ellefsen; \emph{Using Differential Equations to Investigate Invasive Species Management and Cyclical Mating Dynamics}, Earlham College Summer Collaborative Research.
\vspace{-.15cm}\begin{itemize}
\item Internal funding program that supports summer research experiences for undergraduates.
\end{itemize}}\vspace{-.75cm}
%----------------------------------------------------------------------------------------
%	PRESENTATIONS	
%----------------------------------------------------------------------------------------
\section{Presentations and Conferences Since Date of Hire}
\cvitem{February 2023}{SIMIODE Expo Attendee; \emph{A conference for faculty, students, and other parties interested in using modeling to motivate, teach, and learn differential equations}, Virtual.}

\cvitem{April 2023}{Earlham Biology Colloquium; \emph{Mathematical Modeling in Biology}, Richmond, IN.}


%----------------------------------------------------------------------------------------
%	Honors and Awards	
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	PROFESSIONAL MEMBERSHIPS
%----------------------------------------------------------------------------------------

\section{Community Engagement}
\cvitem{AY 2022-2023}{General Education Learning Circle Participant
\vspace{-.15cm}
\begin{itemize}
\item A learning circle focused on assessment which consisted of five meetings, a completed worksheet reflecting on assessment in our classroom, and a product/report to share our reflections with the campus community.
\end{itemize}}
\cvitem{AY 2022-2023}{Re-Launched Earlham's Chapter of Association for Women in Mathematics
\vspace{-.1cm}
\begin{itemize}
\item Association of Women in Mathematics (AWM) is a group for gender-minorities in mathematics. Planned activities have included:  AWM lunches in the dining hall several times a semester, weekend pizza gatherings, an AWM bowling event, and a career panel.
\end{itemize}}
\vspace{-.25cm}
\cvitem{AY 2022-2023}{Assisting Volleyball Graduate Assistant with team statistics
\vspace{-.15cm}\begin{itemize}
\item Attended various meetings with Cal Pringle to share statistics expertise in regards to volleyball data, guide possible analyses that will help advise training, and share data that could possibly be used as examples and projects in the statistics classroom.
\end{itemize}}\vspace{-.35cm}
\cvitem{Spring 2023}{Search Committee Member for Biology's Quantitative Plant Ecologist}


\end{document}

